Exploratory Analysis

### 2023-11-30 Code/Draft1Rmd.Rmd
Updated results

## Difference-in-Difference 
We used a difference-in-difference regression with fixed effects to investigate the impact of drug decriminalization in Oregon counties compared to other states.

@@

```{r results="hide"}
or_yearly2 <- or_yearly
or_yearly2$
```

@@

### Results
Decriminalizing drugs in Oregon has slowed the increase in drug overdose deaths.

>>>>

A synthetic control analysis was conducted using Washington and Oregon as donor states. This analysis has significant limitations due to the lack of donor states and potential lack of credible covariates.
## Difference-in-Difference 
We used a difference-in-difference regression with fixed effects to investigate the impact of drug decriminalization in Oregon counties compared to other states.

@@

@@

### Results

Due to the limitations surrounding our synthetic control analysis, our synthetic Oregon was higher than the actual Oregon pre treatment which should not have happened. This may be due to a lack of accurate covariates used. Our analysis shows synthetic Oregon increasing more than actual Oregon, however limitations have to be noted surrounding this conclusion.

Diff in Diff:

Decriminalizing drugs in Oregon has slowed the increase in drug overdose deaths.
